%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
 
\cvsection{Publications}

\begin{itemize}[leftmargin=*]
	\item
	Yuhui Zhang, \textbf{Ming Li}, Dejun Yang, Jian Tang, Guoliang Xue, and Jia Xu. Trade-off Between Location Quality and Privacy in Crowdsensing: An Optimization Perspective. \textit{IEEE Internet of Things Journal}, 7(4): 3535-3544, 2020.
	
	\item
	Yuhui Zhang, \textbf{Ming Li}, Dejun Yang, Guoliang Xue.
	A Budget Feasible Mechanism for k-Topic Influence Maximization in Social Networks.
	\textit{IEEE Global Communications Conference (GLOBECOM)}, 2019.
	
	\item
	Yuhui Zhang, \textbf{Ming Li}, Dejun Yang, Jian Tang, and Guoliang Xue.
	Optimizing Location Quality in Privacy Preserving Crowdsensing.
	\textit{IEEE Global Communications Conference (GLOBECOM)}, 2019.
	
	\item 
	Jian Lin, Dejun Yang, \textbf{Ming Li}, Jia Xu, and Guoliang Xue. Frameworks for Privacy-Preserving Mobile Crowdsensing Incentive Mechanisms. \textit{IEEE Transactions on Mobile Computing (TMC)}, 17(8): 1851-1864, 2018.
	
	\item 
	\textbf{Ming Li}, Dejun Yang, Jian Lin, Ming Li, and Jian Tang. SpecWatch: A Framework For Adversarial Spectrum Monitoring With Unknown Statistics. \textit{Computer Networks (COMNET)}, 143: 176-190, 2018.
	
	\item 
	Jian Lin, \textbf{Ming Li}, Dejun Yang, and Guoliang Xue. Sybil-Proof Online Incentive Mechanisms for Crowdsensing. \textit{IEEE International Conference on Computer Communications (INFOCOM)}, 2438-2446, 2018.
	
%	\item 
%	\textbf{Ming Li}, Dejun Yang, Jian Lin, Ming Li, and Jian Tang. SpecWatch: A Framework for Adversarial Spectrum Monitoring with Unknown Statistics. CoRR abs/1710.05981 (2017)
	
	\item 
	\textbf{Ming Li}, Jian Lin, Dejun Yang, Guoliang Xue, and Jian Tang. QUAC: Quality-Aware Contract-Based Incentive Mechanisms for Crowdsensing. \textit{IEEE International Conference on Mobile Ad Hoc and Sensor System (MASS)}, 72-80, 2017.
	
	\item 
	Jian Lin, \textbf{Ming Li}, Dejun Yang, Guoliang Xue, and Jian Tang. Sybil-Proof Incentive Mechanisms for Crowdsensing. \textit{IEEE International Conference on Computer Communications (INFOCOM)}, 2017.
	
	\item 
	Michael Brown, Colin Marshall, Dejun Yang, \textbf{Ming Li}, Jian Lin, Guoliang Xue. Maximizing Capacity in Cognitive Radio Networks Under Physical Interference Model. \textit{IEEE/ACM Transactions on Networking (TON)}, 25(5): 3003-3015, 2017.
	
	\item 
	Yuhui Zhang, Dejun Yang, Jian Lin, \textbf{Ming Li}, Guoliang Xue, Jian Tang, and Lei Xie. Spectrum Auctions Under Physical Interference Model. \textit{IEEE Transactions on Cognitive Communications and Networking (TCCN)}, 3(4): 719-728, 2017.
	
	\item 
	\textbf{Ming Li}, Dejun Yang, Jian Lin, Ming Li, and Jian Tang. SpecWatch: Adversarial Spectrum Usage Monitoring in CRNs with Unknown Statistics. \textit{IEEE International Conference on Computer Communications (INFOCOM)}, 2016
	
	\item 
	Jian Lin, Dejun Yang, \textbf{Ming Li}, Jia Xu, and Guoliang Xue. BidGuard: A Framework for Privacy-Preserving Crowdsensing Incentive Mechanisms. \textit{IEEE Conference on Communications and Network Security (CNS)}, 145-153, 2016.
	
	
	
	
	
	
	
	
	
	
	
\end{itemize}




